Stability concerns in random matrices

### 2018-03-29 random_matrix_stability.Rmd
Notes on isolating transforming matrix, and it's lack of fruit

>>>>

I also looked at the matrices that decribe the *changes* between the community matrix with no variation in generation time ($A_{1}$) versus after the addition of generation time ($A_{2}$), which can be described by the transforming matrix ($B$), where,

$$A_{2} = A_{1}B$$
$$A_{1}^{t} A_{2} = A_{1}^{t} A_{1}B$$
$$(A^{t}_{1}A_{1})^{-1}A_{1}^{t} A_{2} = (A^{t}_{1}A_{1})^{-1}A_{1}^{t} A_{1}B$$

$$B = (A^{t}_{1}A_{1})^{-1}A_{1}^{t} A_{2}$$
The transforming matrix B does not appear to have any clear properties when $A_{2}$ stabilises versus destabilises -- its values appear the same, as do the eigenvalues after decomposition. Weird.
